\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-05-31 paper/paper.tex
Start writing cost analysis section

\subsection{Drive-model Comparisons}
We consider the problem of selecting between drive-models. From the
perspective of return on investment, is clear
that we should prefer the drive-models which will provide more years
of service. There are two sources of variation at play; the
posterior uncertainty in the parameters, which largely depends on the
sample size, and the uncertainty in future
observations conditional on the parameters. The {\em posterior
  predictive} distribution incorporates both sources.
\begin{equation}

\end{equation}

>>>>

\subsection{Drive-model Comparisons}
We consider the problem of selecting between drive-models. From a
business perspective, it is clear
that we should prefer the drive-models which will provide more years
of service. For ease of exposition, we will assume that the purchase
price of a hard-drive is the same across drive-models.

There are two sources of variation at play; the
posterior uncertainty in the parameters, which largely depends on the
sample size, and the uncertainty in future
observations conditional on the parameters. The {\em posterior
  predictive} distribution incorporates both sources.
\begin{align*}
  p(t_{d,new}|t) = \int p(\t_{d,new}|\theta_d) p(\theta_d|t) \, d\theta_d\\
\end{align*}
We can sample from this distribution by drawing $t_{d,new}^{(s)}$ from
$\operatorname{GLFP}(\pi_d^{(s)},
\mu_1^{(s)},\sigma_1^{(s)},\mu_{2,d}^{(s)},\sigma_{2,d}^{(s)})$, for
$s=1,...,S$, using the saved posterior draws for the model parameters.

Predicted time to failure does not account for depreciation. Assuming that
antiquated computer hardware tends to have less practical value, we
may want to use a different measure which will reward more the drive-models
that are very reliable in the first 0-5 years compared with those with a
larger number of early failures, but which may last 20 years.
